---
title: "End of The Month Report"
author: "Jeremy Demlow"
date: "May, 2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#Note Your Big Data Class will have you mess up your computer so you might need this in the future
Sys.setenv(JAVA_HOME='...path to JRE...')
Sys.setenv(JAVA_HOME='C:\\Program Files\\Java\\jdk1.8.0_161\\jre')
library(rJava)
library(xlsx)
library(reshape2)
library(stringr)
library(lubridate)
library(stringr)
library(tidyr)
library(xlsx)
library(dplyr)
library(data.table)
library(chron)#dealing with date time
library(Rcpp)
library(RSQLite)
library(sqldf)
library(tcltk2)
library(lubridate)
library(urltools)
```

## BRAC REPORT

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#Input Data
jobs <- read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/alljobs.csv")
brac <- read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/BRAC-LJC_Master.csv")

```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#This is looking at at jobs column "EmployerName" then you are saying change using the function
jobs$EmployerName <- toupper(jobs$EmployerName)
brac$EmployerName <- toupper(brac$EmployerName)
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#SQL Method
filtered <- sqldf::sqldf("Select *
                  from jobs 
                  where EmployerName in (Select EmployerName from brac)")
#This order of columns may change... Verify report matches layout of November 2016
colnames(filtered)
#Currently As of May 4th These are the ones they want. 
brac_jobs <- filtered[,c("DateCreated","Title","EmployerName","IndustryName","City","Education","JobType","NoAvailablePositions")]

brac_jobs$City = as.character(brac_jobs$City)
brac_jobs$City = tolower(brac_jobs$City)
#brac_jobs$City.1 = tolower(brac_jobs$City.1)
brac_jobs$City = ifelse(brac_jobs$City == " ", 'City Not Specified', brac_jobs$City)
```

##BRAC Jobs July_2018 by Education Type Being Sought
```{r, echo=FALSE, warning=FALSE}
brac_jobs %>% 
  group_by(Education) %>%
  summarise(
    Count = n(),
    Percent = round((Count/nrow(brac_jobs)),3)
    ) %>% arrange(desc(Count))
```

##BRAC Jobs July_2018 by Industry Type Having Job Openings
```{r, echo=FALSE, warning=FALSE}
brac_jobs %>% 
  group_by(IndustryName) %>%
  summarise(
    Count = n(),
    Percent = round((Count/nrow(brac_jobs)),3)
  ) %>% arrange(desc(Count))
```

##BRAC Jobs July_2018 by the Job Types 
```{r, echo=FALSE, warning=FALSE}
brac_jobs %>% 
  group_by(JobType) %>%
  summarise(
    Count = n(),
    Percent = round((Count/nrow(brac_jobs)),3)
  ) %>% arrange(desc(Count))
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
Education_Required = brac_jobs %>% 
  group_by(Education) %>%
  summarise(
    Count = n(),
    Percent = round((Count/nrow(brac_jobs)),3)
    ) %>% arrange(desc(Count))

Industury_Type = brac_jobs %>% 
  group_by(IndustryName) %>%
  summarise(
    Count = n(),
    Percent = round((Count/nrow(brac_jobs)),3)
  ) %>% arrange(desc(Count))

Job_Type = brac_jobs %>% 
  group_by(JobType) %>%
  summarise(
    Count = n(),
    Percent = round((Count/nrow(brac_jobs)),3)
  ) %>% arrange(desc(Count))

City_Of_Job= brac_jobs %>%
  group_by(City) %>%
  summarise(
    Count = n(),
    Percent = round((Count/nrow(brac_jobs)),3)
  ) %>% arrange(desc(Count))

```


```{r, echo=FALSE, include = FALSE, warning=FALSE}

write.xlsx(brac_jobs, "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/BRAC-REPORT-July_2018.xlsx",
           sheetName="All_Data", col.names=TRUE, row.names=FALSE, append=FALSE, showNA=FALSE)
write.xlsx(as.data.frame(Education_Required), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/BRAC-REPORT-July_2018.xlsx",sheetName="Education_Required",
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
write.xlsx(as.data.frame(Industury_Type), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/BRAC-REPORT-July_2018.xlsx", sheetName="Industury_Type", 
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
write.xlsx(as.data.frame(Job_Type), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/BRAC-REPORT-July_2018.xlsx", sheetName="Job_Type", 
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
write.xlsx(as.data.frame(City_Of_Job), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/BRAC-REPORT-July_2018.xlsx", sheetName="City_Of_Job", 
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
```


## LJC Job Seeker For The Month Overview

```{r, echo=FALSE, include = FALSE, warning=FALSE}
library(lubridate)
library(dplyr)
job.seeker <- read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/jobseekers.csv", header = T)
```


```{r, echo=FALSE, include = FALSE, warning=FALSE}
str(job.seeker$RegistrationSource)
names(job.seeker) <- tolower(names(job.seeker))

#We need to get the date match the pattern before we can actaully get anything done so we will make objects to allow this to happen. 
date.string <- job.seeker$dateregistered
head(job.seeker$dateregistered)
str(job.seeker$dateregistered)
job.seeker$dateregistered <- as.character(job.seeker$dateregistered)

#Website to see the different type of patterns used: #https://stat.ethz.ch/R-manual/R-devel/library/base/html/strptime.html
date.time <- strptime(date.string, format = "%m/%d/%Y %H:%M:%S") #NOTE THIS CHANGES 

#To help Subesetting we can put this together to allow years to be sepearted with ease
date.year  <- year(date.time)
date.month <- month(date.time)

#add to data set
job.seeker$Reg.Date  <- date.time
job.seeker$Year.Reg  <- date.year
job.seeker$Month.Reg <- date.month
colnames(job.seeker)
#deleting useless columns changes depending on the SQL query they choose
#With issues In March All Data Will Be Given Now
#job.seeker <- job.seeker[ , -c(3:4,12:21)]

#Looking at the last month needs to change every month
date1 <- as.Date("2018-07-01")
date2 <- as.Date("2018-07-31")
interval <- interval(date1, date2)

job.seeker$Reg.Date <- as.Date(job.seeker$Reg.Date)
July_2018.added <- job.seeker[job.seeker$Reg.Date %within% interval,]
```


```{r, echo=FALSE, include = FALSE, warning=FALSE}
Url_Source <- July_2018.added$registrationsource
Url_Source <- as.character(Url_Source)

library(urltools)
url_breakdown <- url_parse(Url_Source)
url_breakdown <- subset(url_breakdown, select = c("path")) 
July_2018.added<- cbind(July_2018.added, url_breakdown)

table(July_2018.added$path)
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
location_data <- read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/jobseekers_latlng.csv", header = TRUE)

#allows names to be lowered
July_2018.added$current.city <- tolower(July_2018.added$current.city)
July_2018.added$current.city <-trimws(July_2018.added$current.city, which = "both")
colnames(July_2018.added)[1] = "id"
colnames(location_data)[1] = "JobSeekerID"
July_2018.added <- merge(x=July_2018.added,
                  y=location_data, 
                  by.x = c("id"),
                  by.y = c("JobSeekerID"),
                  all.x = TRUE,
                  all.y = FALSE)
```

## July_2018 Adds by City
```{r, echo=FALSE, warning=FALSE}
July_2018.added %>%
  group_by(July_2018.added$City) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))
```
## July_2018 Adds by Degree Type
```{r, echo=FALSE, warning=FALSE}
July_2018.added %>%
  group_by(July_2018.added$degree) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))
```

## July_2018 Adds by Resume Completion
```{r, echo=FALSE, warning=FALSE}
July_2018.added %>%
  group_by(July_2018.added$resumecompletefl) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))
```
## July_2018 Adds by Resume Preferred Location
```{r, echo=FALSE, warning=FALSE}
July_2018.added %>%
  group_by(July_2018.added$preferredlocation) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))
```
## July_2018 Adds by Path Location of Sign Up
```{r, echo=FALSE, warning=FALSE}
July_2018.added %>%
  group_by(July_2018.added$path) %>%
  summarise(
    n = n()
  )%>%
  arrange(desc(n))
```

## July_2018 Adds by Current City
```{r, echo=FALSE, warning=FALSE}
July_2018.added %>%
  group_by(July_2018.added$state) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
Cities = July_2018.added %>%
  group_by(July_2018.added$City) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))

Degrees = July_2018.added %>%
  group_by(July_2018.added$degree) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))

Resume_Completed = July_2018.added %>%
  group_by(July_2018.added$resumecompletefl) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))

Preferred_Location = July_2018.added %>%
  group_by(July_2018.added$preferredlocation) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))

PagePath = July_2018.added %>%
  group_by(July_2018.added$path) %>%
  summarise(
    n = n(),
    mean = mean(resumecompletefl)
  )%>%
  arrange(desc(n))

Current_State = July_2018.added %>%
  group_by(July_2018.added$state) %>%
  summarise(
    n = n(), 
    percent = n/nrow(July_2018.added)
  )%>%
  arrange(desc(n))
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#All_Data
write.xlsx(July_2018.added, "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Added_Members.xlsx",
           sheetName="All_Data", col.names=TRUE, row.names=FALSE, append=FALSE, showNA=FALSE)
#Cities
write.xlsx(as.data.frame(Cities),"C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Added_Members.xlsx",
           sheetName="Cities", col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)

write.xlsx(as.data.frame(Degrees), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Added_Members.xlsx",
           sheetName="Degrees",col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
#Resume Complete
write.xlsx(as.data.frame(Resume_Completed),"C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Added_Members.xlsx",
           sheetName="Resume_Completed",col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
#Preferred_Location
write.xlsx(as.data.frame(Preferred_Location), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Added_Members.xlsx",
           sheetName="Preferred_Location",col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
#PagePath
write.xlsx(as.data.frame(PagePath), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Added_Members.xlsx",
           sheetName="PagePath",col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
#Current State
write.xlsx(as.data.frame(Current_State), "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Added_Members.xlsx",
           sheetName="Current_State",col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#Just a check to understand it's working
July_2018.added %>%
  group_by(July_2018.added$state) %>%
  tally() %>% arrange(desc(n))


July_2018.added$path <- as.factor(July_2018.added$path)
July_2018.added$Latitude = as.numeric(July_2018.added$Latitude)
July_2018.added$Longitude = as.numeric(July_2018.added$Longitude)
library(ggplot2)

##There is an issue with this, I probably will not fix this and my advice is use Tabelau to make the Map Chart
##There is some werid issue I might look into, but the Tabelau Map looks 100x better
ggplot(July_2018.added, aes(Longitude, Latitude, colour = path)) + 
  geom_point() +
  coord_quickmap()+
  borders("state")+
  theme_get()+
  ggtitle("Registration For LJC During The Month of July_2018")+
  labs(colour = "Reg Source")
```

```{r, echo=FALSE, warning=FALSE}
library(ggplot2)

##There is an issue with this, I probably will not fix this and my advice is use Tabelau to make the Map Chart
##There is some werid issue I might look into, but the Tabelau Map looks 100x better
ggplot(July_2018.added, aes(Longitude, Latitude, colour = path)) + 
  geom_point() +
  coord_quickmap()+
  borders("state")+
  theme_get()+
  ggtitle("Registration For LJC During The Month of July_2018")+
  labs(colour = "Reg Source")
```

## LJC Employer & Job Seeker Feedback

```{r, echo=FALSE, include = FALSE, warning=FALSE}
EmpFeed = read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/EmployerJobFeedback.csv", header = TRUE)
EmpMis = read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/EmployerMismatchSurvey.csv", header = TRUE)
JobMis = read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/JobSeekerMismatchSurvey.csv", header = TRUE)
```

## Employer Feedback
```{r, echo=FALSE, warning=FALSE}
Emp_Feed = EmpFeed %>%
  group_by(Question, answer)%>%
  summarise(n = n()) %>% mutate(Perc = n/sum(n))%>% 
  arrange(desc(n))

EmpFeed %>%
  group_by(Question, answer)%>%
  summarise(n = n()) %>% mutate(Perc = n/sum(n))%>% 
  arrange(desc(n))

```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#All_Data
write.xlsx(EmpFeed, "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Employer_Feedback.xlsx",
           sheetName="All_Data", col.names=TRUE, row.names=FALSE, append=FALSE, showNA=FALSE)
#Cities
write.xlsx(as.data.frame(Emp_Feed),"C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Employer_Feedback.xlsx",
           sheetName="Reponses", col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
```

## Employer Mismatch Feedback
```{r, echo=FALSE, warning=FALSE}
EmpMis %>% 
  group_by(Reason) %>% summarise(n = n(),mean = round(mean(Match..),1)) %>% 
  arrange(desc(n))

Emp_Mis = EmpMis %>% 
  group_by(Reason) %>% summarise(n = n(),mean = round(mean(Match..),1)) %>% 
  arrange(desc(n))
```

```{r, echo=FALSE, include = FALSE, warning=FALSE}
#All_Data
write.xlsx(EmpMis, "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Employer_MisMatch.xlsx",
           sheetName="All_Data", col.names=TRUE, row.names=FALSE, append=FALSE, showNA=FALSE)
#Cities
write.xlsx(as.data.frame(Emp_Feed),"C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Employer_MisMatch.xlsx",
           sheetName="MisMatch", col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
```

## Job Seeker Mismatch Feedback
```{r, echo=FALSE, warning=FALSE}
JobMis %>% 
  group_by(Reason.For.Mismtch) %>%
  summarise(n = n(), mean = mean(Match..))%>% 
  arrange(desc(n))

Job_Mis = JobMis %>% 
  group_by(Reason.For.Mismtch) %>%
  summarise(n = n(), mean = mean(Match..))%>% 
  arrange(desc(n))
```

```{r, echo=FALSE, warning=FALSE}
#All_Data
write.xlsx(JobMis, "C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Employer_Feedback.xlsx",
           sheetName="All_Data", col.names=TRUE, row.names=FALSE, append=FALSE, showNA=FALSE)
#Emp_Feed
write.xlsx(as.data.frame(Job_Mis),"C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/July_2018_Employer_Feedback.xlsx",
           sheetName="Job_Mis", col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
```

## Information Regarding Resumes

```{r, echo=FALSE, include=FALSE, warning=FALSE}
library(tinytex)
library(lubridate)
library(dplyr)
job.seeker <- read.csv("C:/Users/Jerem/OneDrive/Documents/Vinformatix/Vinformatix_Knowledge_Transfer/LJC/Monthly Reporting/July_2018/jobseekers.csv", header = T)

names(job.seeker) <- tolower(names(job.seeker))

#We need to get the date match the pattern before we can actaully get anything done so we will make objects to allow this to happen. 
date.string <- job.seeker$dateregistered
head(job.seeker$dateregistered)
str(job.seeker$dateregistered)
job.seeker$dateregistered <- as.character(job.seeker$dateregistered)

#Website to see the different type of patterns used: #https://stat.ethz.ch/R-manual/R-devel/library/base/html/strptime.html
date.time <- strptime(date.string, format = "%m/%d/%Y %H:%M:%S")

#To help Subesetting we can put this together to allow years to be sepearted with ease
date.year  <- year(date.time)
date.month <- month(date.time)

#add to data set
job.seeker$Reg.Date  <- date.time
job.seeker$Year.Reg  <- date.year
job.seeker$Month.Reg <- date.month
Url_Source <- job.seeker$registrationsource
Url_Source <- as.character(Url_Source)

library(urltools)
url_breakdown <- url_parse(Url_Source)
url_breakdown <- subset(url_breakdown, select = c("path")) 
job.seeker<- cbind(job.seeker, url_breakdown)
#colnames(job.seeker)
#deleting useless columns changes depending on the SQL query they choose
#job.seeker <- job.seeker[ , -c(4,6:7,11:21,27,29,33,35:36)]
rm(Url_Source, url_breakdown)

#Looking at the last month needs to change every month
date1 <- as.Date("2018-07-01")
date2 <- as.Date("2018-07-31")
interval <- interval(date1, date2)

str(job.seeker$Reg.Date)
job.seeker$Reg.Date <- as.Date(job.seeker$Reg.Date)
Last6.added <- job.seeker[job.seeker$Reg.Date %within% interval,]
Url_Source <- Last6.added$registrationsource
Url_Source <- as.character(Url_Source)

#Resume
date.string <- Last6.added$resume.post.date
Last6.added$resume.post.date <- as.character(Last6.added$resume.post.date)
date.time <- strptime(date.string, format =  "%m/%d/%Y %H:%M:%S")
Last6.added$Resume.Date  <- date.time

#Access
date.string <-Last6.added$profile.accessed
Last6.added$profile.accessed <- as.character(Last6.added$profile.accessed)
date.time <-strptime(date.string, format =  "%m/%d/%Y %H:%M")
Last6.added$access.Date <-date.time
#colnames(Last6.added)
#Last6.added <- Last6.added[, -c(5,10,15)]

#Subset Resumes/Non-Resumes
df <- subset(Last6.added, Last6.added$resumecompletefl == 1)
df_na <- subset(Last6.added, Last6.added$resumecompletefl == 0)
rm(job.seeker, date.month, date.string, date.year, date1, date2, interval, date.time,Url_Source)

#Note there is system error with ljc picking up resumes before registration dates 
df$Res_lapse <- round(difftime(df$Resume.Date, df$Reg.Date, units = "days"),1)
df$Res_lapse  <- as.numeric(df$Res_lapse)
df$Res_lapse  <- ifelse(df$Res_lapse < 1, 0, df$Res_lapse)
df$rightaway <- ifelse(df$Res_lapse  == 0, "1", "0")
```

## **Who Is Completing Their Resumes**

```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
#colnames(Last6.added)
Last6.added$access.Date <- as.POSIXct(Last6.added$access.Date)
Last6.added$Resume.Date <- as.POSIXct(Last6.added$Resume.Date)
Last6.added$resumecompletefl= as.factor(Last6.added$resumecompletefl)
Last6.added$degree = as.character(Last6.added$degree)
Last6.added$degree[Last6.added$degree==" "]<-"Missing"
Last6.added$degree = as.factor(Last6.added$degree)

Last6.added %>%
  subset(!(Last6.added$degree == "Missing")) %>%
  group_by(resumecompletefl,degree) %>%
  summarise(
    count = n()
  )%>% group_by(degree)%>%
  mutate(freq = paste0(round(100 * (count / sum(count)),2), "%")) %>%
  filter(count>0) %>% arrange(degree)%>%
  ggplot( aes(x = resumecompletefl, y = count, fill = degree)) +
  geom_bar(stat = "identity", color = "black")+
  geom_text(aes(label = freq, vjust= 1))+
  facet_wrap(~degree, scale = "free_y")+ 
  theme_light() + 
  theme(legend.position = "none")+
  labs(title = "Resume Completed By Degree Type",
       caption = "1 = Resume Completed & 0 = Resume Incomplete", 
       x = "Resume Complete Or Not")

Last6.added %>%
  group_by(resumecompletefl,path) %>%
  summarise(
    count = n()
  ) %>% group_by(path) %>%
  mutate(freq = paste0(round(100 * (count/sum(count)),2), "%"))%>%
  filter(count > 0 ) %>% arrange(desc(count))%>%
  ggplot( aes(x = resumecompletefl, y = count, fill = path)) +
  geom_bar(stat = "identity", color = "black")+
  geom_text(aes(label = freq, vjust= 1))+
  facet_wrap(~path, scale = "free_y")+ 
  theme_light() + 
  theme(legend.position = "none")+
  labs(title = "Resume Completed By Page Path",
       caption = "1 = Resume Completed & 0 = Resume Incomplete", 
       x = "Resume Complete Or Not")

```

## **LJC Activity, Time it Takes For Resumes to be Completed & Time Since Last Visit**


```{r, echo=FALSE, warning=FALSE}
library(dplyr)
df$access.Date <- as.POSIXct(df$access.Date)
df$Resume.Date <- as.POSIXct(df$Resume.Date)
table(df$rightaway)
summary(df$Res_lapse)

df$Res_lapse %>%
  subset(df$Res_lapse > 1 & df$Res_lapse < 20) %>%
  summary(df$Res_lapse)

```


```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
df %>%
  subset(df$Res_lapse > 1) %>%
  ggplot(aes(x = Res_lapse)) +
  geom_bar(color = "blue")+
  theme_light()+
  labs(title = "Distrubtion of Lasped Time In Day for Resume Completion",
       subtitle = "LJC Members", x = "Lapsed Time In Days", y ="Frequency")

ggplot(subset(df, !(df$Res_lapse <= 3)), aes(y =Res_lapse, x = path, color = path))+
  geom_boxplot()+
  theme_light()+
  ggtitle("Number of Days by Reg Source to Complete Thier Resume", 
          "Showing only Observations with Days Lasped of 3 or greater")+
  xlab("Registration Source")+
  ylab("Number Of Days")+ 
  theme(axis.text.x = element_text(angle = 50, hjust = 1, size = 7))
```

## **Looking At The Number of Applications**

```{r, echo=FALSE, warning=FALSE}
df_na$Res_lapse <- -1
df_na$rightaway <- -1
df = rbind(df, df_na)

#Calcuate How Many Days This Indvidual Has Been A Member
df$Membership_days <- round(difftime(Sys.Date(), df$Reg.Date, units = "days"),0)
#df$Membership_days <- ifelse(df$Membership_days < 1, 0, df$Membership_days)
df$Membership_days <- as.numeric(df$Membership_days)

#Time since they were last on the LJC Website
df$visit_lapse <- round(difftime(Sys.Date(), df$access.Date, units = "days"), 0)
df$visit_lapse <- ifelse(df$visit_lapse < 1, 0, df$visit_lapse)
df$visit_lapse <- as.numeric(df$visit_lapse)


df$Re_Visit <- ifelse(df$Membership_days == df$visit_lapse, 0, 1)
#Metric to messure if the number of days between last visit and membership days 
#This is going to give us a metric to know how long since they signed up and their last visit
#ie: if you have 87 days it means that you became a memember 87 days ago and have come back x amount of days later
#Kinda of a metric to give us an idea of how many people come back (Explore this more later)
df$Days <- df$Membership_days - df$visit_lapse

df_na$Membership_days <- 0
df_na$visit_laspe <- -1
df_na$Re_Visit <- 0
df_na$Days <- -1

#table(df$Re_Visit)

#mean(df$visit_lapse)

df %>% 
  group_by(df$Re_Visit) %>%
  summarise(
    Total = n(),
    Avg_LastVisit = mean(visit_lapse),
    Apps_Sent = sum(applicationcount)
  )

df$check<-as.factor(df$Re_Visit)
```


```{r  , echo=FALSE}
library(ggplot2)
ggplot(df, aes(visit_lapse, fill = path)) +
  stat_bin(geom = "bar", bins = 50, alpha = .58)+
  facet_wrap(~path, scales="free_y")+
  theme_light()+
  theme(legend.position ="none")+
  labs(title = "Distrubtion of Time Since Last Visit In Days")

plot = df %>% 
  group_by(path) %>% 
  summarise(
    n = n(), 
    min = min(visit_lapse), 
    max = max(visit_lapse), 
    mean = mean(visit_lapse),
    median = median(visit_lapse),
    Apps = sum(applicationcount)
  ) %>%
   arrange(desc(mean))

ggplot(plot, aes(x = reorder(path, -mean), y = n, fill = path)) +
  geom_bar(stat = "identity")+
  xlab("Reg Source")+
  geom_text(aes(label= round(mean), vjust=-.3))+
  theme_light()+
  theme(axis.text.x = element_text(angle = 40, hjust = 1, size = 7), legend.position = "none")+
  labs(title = "Ordered by Average Days Since Last Visiting LJC", 
       subtitle = "Numbers Above Bars Represents the Mean Days Since Logging Back on LJC",
       x = "Registration source", y = "Amount Of LJC Members")
```


```{r,echo=FALSE, include = FALSE, warning=FALSE}
Last6.added %>%
  group_by(resumecompletefl)%>% 
  summarise(
    apps = sum(applicationcount)
  )

df %>% 
  summarise(
    n = sum(is.na(df$Resume.Date))
  )
```

